\begin{description}
\item[Project] \hfill \\
A project is basically a collection of activities. Is has an assigned managing user, a name and a man-hour budget.  

\item[Activity] \hfill \\
The activity is what constitues actual work tasks in a project. They each have their own hour budget and description. Developers can be assigned to work on activities, and they register time by choosing which activity that entry belongs to.

\item[Fixed activity] \hfill \\
A fixed activity is just an activity, but it is not linked to a specific project. Instead it is a way for users to register time that has no project reference, but instead is either due to sickness, vacation, courses, etc.

\item[Developer] \hfill \\
All users in the system are also (or can be) developers. They are the ones who register time, create users, projects and generally maintain the system. Nothing can be accessed without a valid login. They have their names and initials stored.

\item[Project Manager] \hfill \\
The project manager is just a user, who is assigned as a manager on a project. They are the ones who are responsible for activities in a project and assigns developers to work on specific activites.

\item[Assistance] \hfill \\
A developer may ask another developer to help out on an activity. The assisting user then registers the used time normally, except he/she now flags the entry as an assist. A user does not need to be assigned to an activity to assist on it.

\item[Budgets] \hfill \\
All budgets in the system are represented by a number of hours that a project or activity is estimated to last. There is both project budgets and activity budgets so that the project managers can easily see how much of a project budget is currently estimated to be used by current activities.

\item[Report] \hfill \\
The project report is a screen in which the project managers can view statistics about the project. There are figures and numbers describing how much of the budget is in use, how much time is estimated to be left and how much time has been registered to that project in total.

\end{description}